Compilation With Program Synthesis

### 2023-08-21 new-paper/paper.tex
clarify with formatting
typo
a small fix

\begin{lstlisting}
Sll : layout(List)
Sll Nil := emp;
Sll (Cons head tail) :=
  x :-> head ** (x+1) :-> nxt ** Sll tail [nxt];
\end{lstlisting}

@@

\begin{lstlisting}
Sll : @(s : set) layout(List);
Sll Nil := s == {} ;; emp;
Sll (Cons head tail) :=
  s == {head} ++ s1
    ;;
  x :-> head ** (x+1) :-> nxt ** Sll tail @s1 [nxt];
\end{lstlisting}

@@

\begin{lstlisting}
synth append :
  (s == (s1 ++ s2))
    ;;
  Sll @s1 -> Sll @s2 -> Sll @s
\end{lstlisting}

>>>>

\begin{lstlisting}
Sll : layout[x](List)
Sll Nil := emp;
Sll (Cons head tail) :=
  x :-> head ** (x+1) :-> nxt
    ** Sll tail [nxt];
\end{lstlisting}

@@

\begin{lstlisting}
Sll : @(s : set) layout[x](List);
Sll Nil := s == {} ;; emp;
Sll (Cons head tail) :=
  s == {head} ++ s1
    ;;
  x :-> head ** (x+1) :-> nxt
    ** Sll tail @s1 [nxt];
\end{lstlisting}

@@

\begin{lstlisting}
synth append :
  (s == (s1 ++ s2))
    ;;
  Sll @s1 -> Sll @s2 -> Sll @s;
\end{lstlisting}
